Dissertation reading notes

### 2023-11-16 Texfiles/Notes.tex
Potential finish
post submit edits

@@

>>>>

\subsection{2023-11-15}
\begin{itemize}
      \item Making a list of things to change and update.
      \item Regressions -- I need to add the RV into the regression equations. I
            guess I am actually a bit confused at what I think the RV is -- did I use
            expected retirement age? I used retirement year.

      \item I need to make the case that retirement is sticky?
      \item I need to add retirement year as a RV -- this is a first order
            mistake I think.
\end{itemize}

@@

% \subsection{Rough plan}
% \begin{itemize}
%     \item Intro
%           \begin{enumerate}
%               \item "Latest data from HM Revenue Customs (published in April)
%                     showed more than £45bn has been taken from pots since 2015."
%                     https://www.ftadviser.com/pensions/2022/02/08/pension-freedoms-were-they-really-a-good-idea/
%               \item what portion of savings are because of retirement savings?
%               \item Also talk about heterogeneity across countries. Some
%                     countries want to move towards more annuitisation. This
%                     annual review is a good source of info
%                     \cite{banks_crawford_ar_2022}
%               \item https://www.moneysavingexpert.com/savings/pension-freedom/
